---
title: 'R Example LASSO: Wages'
output:
  html_document:
    df_print: paged
---


```{r}
library(glmnet)
library(plotmo) # for plot_glmnet
library(dplyr)
library(expss)
library(qpcR)


# Set random number seed
set.seed(40)
## Clear workspace 
#rm(list = ls())
```

Add labels to get better overview of vars included
```{r}
#apply labels to get overview
SampleIV <- apply_labels(SampleIV,q1_adopt="Adoption mechanical weeding binary",
                    fields_b="observing fields binary",
                    info_b="knowing adopters binary",
                    minDist_demo="minimal distance to demonstration farm",
                    sq.demodist="squared minimal distance to demonstration farm",
                    Fabrikstandort_agg="sugar factory location aggregated",
                    farmsize_b="farm size in ha over 50 binary",
                    AES_b="participation in AES binary",
                    age_b="farmer age over 45 binary",
                    farm_organic="production type binary",
                    meanFarmSize2="mean farm size at county level",
                    UAA_unter5="UAA in farms with less than 5ha at county level",
                    UAA_Sugarbeet="UAA where sugarbeet is grown at county level",
                    SB_region="share of SB in UAA larger 10% binary",
                    ShareSB="Share of UAA for Sugarbeets in arable UAA at county level",
                    lwBetr_Anzahl="number of farms in county",
                    lwBetrOrganic_Anzahl="number of farms with organic agriculture at county level",
                    lwBetrUnter5_Anzahl="number of farms with less than 5ha at county level",
                    lwBetr5b10_Anzahl="number of farms with 5-10ha at county level",
                    UAA_5b10="UAA in farms with 5- 10ha at county level",
                    UAA="UAA at county level",
                    UAA_Organic="organic UAA at county level",
                    UAA_arable="arable UAA at county level",
                    ShareOrgFarms="Share of organic farms in all farms at county level",
                    ShareOrgArea="Share of organic area in UAA at county level",
                    Area="total area county",
                    population="Number of habitants at county level",
                    populationdensity="habitants per sq.km",
                    farmDens="farms per sq.km",
                    areaDens="UAA per total county area",
                    ShareSmallFarms="Share of small farms (< 10ha) in all farms at county level",
                    elevation_in_m_mean="mean elevation at county or field level",
                    sand_content_percent_mean="mean sand content in soil at county or field level",
                    clay_content_percent_mean="mean clay content in soil at county or field level",
                    sq.elevation_in_m_mean="sq.mean elevation at county or field level",
                    sq.sand_content_percent_mean="sq.mean sand content in soil at county or field level",
                    sq.clay_content_percent_mean="sq.mean clay content in soil at county or field level",
                    mainly_crop="farm specialized in crops/ arable farming binary",
                    Verband_agg = "producer associations aggregated",
                    meanDist = "mean distance to other farmers' fields, set to 50 for NA",
                    sq.meanDist ="squared mean distance to other farmers' fields",
                    fields_dist ="interaction of fields_b*meanDist =0 for non-observators",
                    sq.fields_dist = "squared distance to other farmers' fields with 0 for non-observators",
                    ShareSmallArea= "share of area of farms wih 5 to 10 ha in total UAA",
                    ShareArableUAA = "share of arable area in total UAA", 
                    ShareArableInTotalArea = "share of arable area in total county area")

```


Get explanatory variables and create subsample including dependant and independant variable
```{r}
dat<-SampleIV %>% dplyr::select("q1_adopt","fields_b","info_b","minDist_demo","sq.demodist","farmsize_b","AES_b","age_b","farm_organic","mainly_crop", "meanFarmSize2","ShareOrgFarms","ShareOrgArea","populationdensity","farmDens","areaDens","ShareSmallFarms","elevation_in_m_mean","sand_content_percent_mean","clay_content_percent_mean","sq.elevation_in_m_mean","sq.sand_content_percent_mean","sq.clay_content_percent_mean", "ShareArableUAA", "ShareArableInTotalArea","Fabrikstandort_agg")

#take kreislevel data away:
#


XVars <- c("fields_b","info_b","minDist_demo","sq.demodist","farmsize_b","AES_b","age_b","farm_organic","mainly_crop", "meanFarmSize2","ShareOrgFarms","ShareOrgArea","populationdensity","farmDens","areaDens","ShareSmallFarms","elevation_in_m_mean","sand_content_percent_mean","clay_content_percent_mean","sq.elevation_in_m_mean","sq.sand_content_percent_mean","sq.clay_content_percent_mean", "ShareArableUAA", "ShareArableInTotalArea","Fabrikstandort_agg")


df <-dat[XVars]

df<-df %>% drop_na()
dat<-dat %>% drop_na()
```

get overview of vars/ group of vars
```{r}
vars.prereg <- SampleIV %>% dplyr::select("q1_adopt","fields_b","info_b","fields_dist","sq.fields_dist","minDist_demo","sq.demodist","Fabrikstandort_agg","farmsize_b","AES_b","age_b")

vars.prereg_extended <-SampleIV %>% dplyr::select("q1_adopt","fields_b","info_b","fields_dist","sq.fields_dist","minDist_demo","sq.demodist","Fabrikstandort_agg","farmsize_b","AES_b","age_b", "SB_region","meanFarmSize2","sand_content_percent_mean","elevation_in_m_mean")

vars.all_lasso <-SampleIV %>% dplyr::select("q1_adopt","fields_b","info_b","minDist_demo","sq.demodist","Fabrikstandort_agg","farmsize_b","AES_b","age_b","farm_organic","SB_region","meanFarmSize2","UAA_unter5","UAA_Sugarbeet","ShareSB","lwBetr_Anzahl","lwBetrOrganic_Anzahl","lwBetrUnter5_Anzahl","lwBetr5b10_Anzahl","UAA_5b10","UAA","UAA_Organic","UAA_arable","ShareOrgFarms","ShareOrgArea","Area","population","populationdensity","farmDens","areaDens","ShareSmallFarms","elevation_in_m_mean","sand_content_percent_mean","clay_content_percent_mean","sq.elevation_in_m_mean","sq.sand_content_percent_mean","sq.clay_content_percent_mean","mainly_crop", "Verband_agg")

vars.identified11 <-SampleIV %>% dplyr::select("q1_adopt","fields_b","info_b","minDist_demo","Fabrikstandort_agg","farmsize_b","AES_b","age_b","sand_content_percent_mean")

vars.identified8 <-SampleIV %>% dplyr::select("q1_adopt","fields_b","info_b","minDist_demo","Fabrikstandort_agg","farmsize_b","AES_b","age_b","sand_content_percent_mean","farm_organic","ShareSB","lwBetr_Anzahl","UAA_Organic","population","populationdensity","areaDens","ShareSmallFarms","sq.sand_content_percent_mean","SB_region")



vtable(dat, missing = TRUE)

```


### Run lasso on the model directly 

```{r}

lasso_mod <- glmnet(df,dat$q1_adopt,alpha=1, family='binomial')
plot_glmnet(lasso_mod, label=15)
```

Run cross-validation for model selection

```{r}
cvfit <- cv.glmnet(data.matrix(df),dat$q1_adopt, nfolds=40,family='binomial', type.measure = "class")

plot(cvfit)
```
Get the model with the lowest error (indicated be the left vertical 
line in the plot)
```{r}

coef(cvfit ,s ="lambda.min")
```
```{r}
coef(cvfit ,s ="lambda.1se")
```
**Interpretation**
 



## Double selection approach 


See: 
*Belloni, Alexandre, Victor Chernozhukov, and Christian Hansen. 2014. “High-Dimensional Methods and Inference on Structural and Treatment Effects.” The Journal of Economic Perspectives 210 (2): 210–50.*

Lets see how a double selection approach would work in this context. 
Remember that we are interested in estimating the effects of info/field on adoption.
Hence in this example info/field is our "treatment" variable. 
In the double selection approach we first run two models. 
1) We explain adoption by all control variables (except info and field)
2) We explain info by all the control variables
3) We explain field by all the control variables
In each case we use LASSO for variable selection. 

Finally we run run OLS on the union of the variables selection in 1), 2) and 3)
First get all the exogenous variables (excluding info and field)
```{r}
dfExog <- df[ , !names(df) %in% c("info_b", "fields_b")]
#create df for corss-check for fields w/o info
dfExog2 <- df[ , !names(df) %in% c("info_b")]
dfExog3 <- df[ , !names(df) %in% c("fields_b")]
```

### 1) Perform model selection explaining adoption by all the exogenous variables 
(excluding info and field)
```{r}
# Run cross validation
cvfit_AdoptExog <- cv.glmnet(data.matrix(dfExog), dat$q1_adopt,nfolds=40, family = "binomial",type.measure = "class")
plot(cvfit_AdoptExog)
```

Get list of variables for "lambda.min"
```{r}
coefAdoptmin <- coef(cvfit_AdoptExog ,s ="lambda.min")
coefAdoptmin
lstCoefAdoptmin <- coefAdoptmin@Dimnames[[1]][which(coefAdoptmin != 0 ) ] #feature names: intercept included
lstCoefAdoptmin <- tail(lstCoefAdoptmin,-1) # exclude constant
lstCoefAdoptmin
```

Get list of variables for "lambda.1se" 
```{r}
coefAdopt1se <- coef(cvfit_AdoptExog ,s ="lambda.1se")
coefAdopt1se
lstCoefAdopt1se <- coefAdopt1se@Dimnames[[1]][which(coefAdopt1se != 0 ) ] #feature names: intercept included
lstCoefAdopt1se <- tail(lstCoefAdopt1se,-1) # exclude constant
lstCoefAdopt1se

```

### 2) Perform model selection explaining info by all the exogenous variables 


```{r}
# Run cross validation
cvfit_info <- cv.glmnet(data.matrix(dfExog), dat$info_b,nfolds=40,family = "binomial",type.measure = "class")
plot(cvfit_info)
```

Get list of variables for "lambda.min"
```{r}
coefinfomin <- coef(cvfit_info ,s ="lambda.min")
coefinfomin
lstCoefinfomin <- coefinfomin@Dimnames[[1]][which(coefinfomin != 0 ) ] #feature names: intercept included
lstCoefinfomin <- tail(lstCoefinfomin,-1) # exclude constant
lstCoefinfomin

```

Get list of variables for "lambda.1se" 
```{r}
coefinfo1se <- coef(cvfit_info ,s ="lambda.1se")
coefinfo1se
lstCoefinfo1se <- coefinfo1se@Dimnames[[1]][which(coefinfo1se != 0 ) ] #feature names: intercept included
lstCoefinfo1se <- tail(lstCoefinfo1se,-1) # exclude constant
lstCoefinfo1se
```

### 3) Perform model selection explaining fields by all the exogenous variables 


```{r}
# Run cross validation
cvfit_fields <- cv.glmnet(data.matrix(dfExog), dat$fields_b,nfolds=40,family = "binomial",type.measure = "class")
plot(cvfit_fields)
#cross-check full model on fields
reg_Fullfields <- glm(fields_b ~ .,data=dfExog2,family = "binomial")
summary(reg_Fullfields)
m.reg_Fullfields_mfx <-probitmfx(reg_Fullfields, data = dfExog2)
m.reg_Fullfields_mfx
plot_summs(m.reg_Fullfields_mfx, robust = TRUE, scale = TRUE)

#cross-check full model on info
reg_Fullinfo <- glm(info_b ~ .,data=dfExog3,family = "binomial")
summary(reg_Fullinfo)
m.reg_Fullinfo_mfx <-probitmfx(reg_Fullinfo, data = dfExog3)
m.reg_Fullinfo_mfx
plot_summs(m.reg_Fullinfo_mfx, robust = TRUE, scale = TRUE)
```

Get list of variables for "lambda.min"
```{r}
coeffieldsmin <- coef(cvfit_fields ,s ="lambda.min")
coeffieldsmin
lstCoeffieldsmin <- coeffieldsmin@Dimnames[[1]][which(coeffieldsmin != 0 ) ] #feature names: intercept included
lstCoeffieldsmin <- tail(lstCoeffieldsmin,-1) # exclude constant
lstCoeffieldsmin

```

Get list of variables for "lambda.1se" 
```{r}
coeffields1se <- coef(cvfit_fields ,s ="lambda.1se")
coeffields1se
lstCoeffields1se <- coeffields1se@Dimnames[[1]][which(coeffields1se != 0 ) ] #feature names: intercept included
lstCoeffields1se <- tail(lstCoeffields1se,-1) # exclude constant
lstCoeffields1se
```


### Run the final model explaining Adoption by the union of variables selected in 1), 2) and 3). 

Because we are worried about omitted variables bias lets take the variables 
selected from the "lambda.min" this includes more variables as "lambda.1se".
Because including too many variables is less of a problem then excluding 
relevant once we want to be more conservative here. 

```{r}
#save lists of vars selected in different steps
lstvarsselected3_kreisdummy <- lst(lstCoefAdoptmin,lstCoeffieldsmin,lstCoefinfomin)

dfDouble1 <- dat[,union(union(lstCoeffieldsmin,lstCoefAdoptmin),c("q1_adopt","fields_b"))]
dfDouble2 <- dat[,union(union(lstCoefinfomin,lstCoefAdoptmin),c("q1_adopt", "info_b"))]
dfDouble3 <- dat[,union(union(lstCoefinfomin,lstCoeffieldsmin),c("fields_b", "info_b"))]

dfDouble <- cbind(dfDouble1,dfDouble2,dfDouble3)
dfDouble <-dfDouble %>% 
  dplyr::select(unique(colnames(.)))

reg_double3_kreisdummy <- glm(q1_adopt ~ .,data=dfDouble, family = "binomial")
summary(reg_double3_kreisdummy)
df.Lasso_selected3_kreisdummy <- reg_double3_kreisdummy[["model"]] 
vtable(df.Lasso_selected3_kreisdummy, values = TRUE, missing = TRUE)
#marginal effects
m.Lasso_select_mfx3_kreisdummy <-probitmfx(reg_double3_kreisdummy, data = dfDouble)
m.Lasso_select_mfx3_kreisdummy
coefs_3_kreisdummy <-  m.Lasso_select_mfx3_kreisdummy[["mfxest"]]
```
Compare that to the result that we would obtained for OLS on all variables
```{r}
reg_Full3_kreisdummy <- glm(q1_adopt ~ .,data=dat,family = "binomial")
summary(reg_Full3_kreisdummy)
m.reg_Full3_kreisdummy_mfx <-probitmfx(reg_Full3_kreisdummy, data = dat)
m.reg_Full3_kreisdummy_mfx
```


Compare model results visually, e.g. estimates for info_b and fields_b
```{r}
#with max N
plot.reg_compare <- plot_summs(m.Full.comp_mfx3,
                           #  m.Full.IV_mfx,
                            #  m.Full_regional_mfx2,
                              m.reg_Full1.0_verband_mfx,
                             m.reg_Full1.0_fabric_mfx,
                             m.Lasso_select_mfx1.0_verband,
                              m.Lasso_select_mfx1.0_fabric,
                              #m.Lasso_select_mfx3.1_verband,
                              m.Lasso_select_mfx1.1_fabric,
                             # m.Lasso_select_mfx1.2_verband,
                              m.Lasso_select_mfx1.2_fabric,
                              #m.Lasso_select_mfx3.3_verband,
                              m.Lasso_select_mfx1.3_fabric,
                              m.Lasso_select_mfx1.4_fabric,
                              m.Lasso_select_mfx1.5_fabric,
                              m.Lasso_select_mfx1.6_fabric,
                            #  m.reg_Full2_kreisdummy_mfx,
                            #  m.reg_Full3_kreisdummy_mfx,
                               coefs = c("knowing other farmers (info)"="info_b1",
                    "Info_IV =knowing other farmers"="info_iv",
                     "observing fields (fields)"="fields_b1",
                      "Field_IV = observing fields"="fields_iv"),
       colors = c("Grey","Grey","Green","Blue","Red","Orange","Brown","Black","Pink","Purple", "yellow", "darkgreen", "lightblue", "darkblue", "lightgreen", "red4"),#c("Spectral"),
           legend.title = "marginal effects",
        model.names = c("M_prereg", 
                       #  "M_preregIV", 
                        #"M_prereg_extended", 
                        "FullM1.0_verband",
                        "FullM1.0_fabric",
                        "LassoM1.0_verband_s20nf20",
                        "LassoM1.0_fabric_s20nf20",
                        #"LassoM3.1_verband_s40nf20",
                        "LassoM1.1_fabric_s40nf20",
                        #"LassoM3.2_verband_s20nf10",
                        "LassoM1.2_fabric_s20nf10",
                        #"LassoM3.3_verband_s40nf40",
                        "LassoM1.3_fabric_s40nf40",
                       "LassoM1.4_fabric_s20nf40",
                        "LassoM1.5_fabric_s200nf40",
                        "LassoM1.6_fabric_s40nf80" 
                        #"FullM3.8_kreisdummy"
                      
               ),
           scale = TRUE, robust = TRUE) + theme(legend.position="bottom")

plot.reg_compare
```

```{r}

#reg double
plot.reg_double <- plot_summs(reg_double1,reg_double2,reg_double3,reg_double4,reg_double5,reg_double6,reg_double7,
           coefs = c("knowing other farmers (info)"="info_b1",
                     "observing fields (fields)"="fields_b1"),
         colors = c("Spectral"),
         model.names = c("M1_s20nf20","M2_s40nf20","M3_s20nf10","M4_s40nf40","M5_s20nf40","M6_s40nf10"),
           scale = TRUE, robust = TRUE)


plot.reg_double_vars <- plot_summs(reg_double4,reg_double7,reg_double8,reg_double9,reg_double10,reg_double11,reg_double12,m.Full.IV,m.Full.comp,m.Full_regional,reg_double13,reg_double14,
           coefs = c("knowing other farmers (info)"="info_b1",
                     "Info_IV =knowing other farmers"="info_iv",
                     "observing fields (fields)"="fields_b1",
                      "Field_IV = observing fields"="fields_iv"),
         colors = c("Spectral"),
         model.names = c("M4_s40nf40","M7_s40nf40_prereg","M8_s40nf40_prereg_extended","M9_s40nf40_prereg_extended_nofieldsdist","M10_s40nf40_allLasso_wfieldsdist","M11_s40nf40_allLasso_wfieldsdist_noverbagg","M12_s40nf40__allLasso_nofieldsdist_noverbagg","M_preregIV", "M_prereg_noIV", "M_prereg_extended", "M13_vars_identified", "M14_vars_identified" ),
           scale = TRUE, robust = TRUE) + theme(legend.position="bottom")

plot.reg_old <- plot_summs(m.Full.IV,m.Full.comp,m.Full_regional,
           coefs = c("knowing other farmers (info)"="info_b1",
                     "Info_IV =knowing other farmers"="info_iv",
                     "observing fields (fields)"="fields_b1"),
                     "Field_IV = observing fields"="fields_iv",
         colors = c("Spectral"),
         model.names = c("M_preregIV", "M_prereg_noIV", "M_prereg_extended" ),
           scale = TRUE, robust = TRUE) 
#reg full
plot.reg_Full <- plot_summs(reg_Full1,reg_Full2,reg_Full3,reg_Full4,reg_Full5,reg_Full6,reg_Full7,reg_Full8,reg_Full9,reg_Full10,reg_Full11,reg_Full12,m.Full.IV,m.Full.comp,   
           coefs = c("knowing other farmers (info)"="info_b1",
                     "observing fields (fields)"="fields_b1"),
           model.names = c("M1_s20nf20","M2_s40nf20","M3_s20nf10","M4_s400nf40","M5_s20nf40","M6_s40nf10","M7_s40nf40_prereg","M8_s40nf40_prereg_extended","M9_s40nf40_prereg _extended_nofieldsdist","M10_s40nf40_allLasso_wfieldsdist","M11_s40nf40_allLasso_wfieldsdist_noverbagg","M12_s40nf40__allLasso_nofieldsdist_noverbagg","M_preregIV", "M_prereg_noIV", "M_prereg_extended" ),
          colors = "Spectral",
           scale = TRUE, robust = TRUE)
```
Which vars have been selected in all specifications?
```{r}
#make all teh same nr rows

VarsSelected <-cbind(df.Lasso_selected1.0_fabric,df.Lasso_selected1.1_fabric,df.Lasso_selected1.2_fabric, df.Lasso_selected1.3_fabric, df.Lasso_selected1.4_fabric, df.Lasso_selected1.5_fabric,df.Lasso_selected1.6_fabric,df.Lasso_selected1.0_verband)

VarsSelected <- VarsSelected[-c(2:205), ]
VarsSelected <- as.data.frame(t(VarsSelected))
library(tibble)
VarsSelected <- tibble::rownames_to_column(VarsSelected, "variable")

VarsSelected<- VarsSelected %>% dplyr::group_by(variable) %>% dplyr::mutate(n = n())
VarsSelected <- VarsSelected[,-c(2,3)]

VarsSelected$variable <-  sub("*\\.[0-9]", "", VarsSelected$variable)
VarsSelected$variable <- lapply(VarsSelected$variable, function(x) gsub("0", "", x))
VarsSelected$variable <- lapply(VarsSelected$variable, function(x) gsub("1", "", x))

VarsSelected <-VarsSelected %>% 
  dplyr::count(variable)
VarsSelected <-VarsSelected[order(VarsSelected$n, decreasing =TRUE),]  

stargazer(VarsSelected,                 # Export txt
          summary = FALSE,
        type = "html",
          out = "VarsSelectedLasso.html")


#identify vars only chosen in step 1 (adoption)
df1.0f<- as.data.frame(lstvarsselected1.0_fabric[["lstCoefAdoptmin"]])
df1.0v<- as.data.frame(lstvarsselected1.0_verband[["lstCoefAdoptmin"]])
df1.1f<- as.data.frame(lstvarsselected1.1_fabric[["lstCoefAdoptmin"]])
#df3.1v<- as.data.frame(lstvarsselected1.1_verband[["lstCoefAdoptmin"]])
df1.2f<- as.data.frame(lstvarsselected1.2_fabric[["lstCoefAdoptmin"]])
#df3.2v<- as.data.frame(lstvarsselected1.2_verband[["lstCoefAdoptmin"]])
df1.3f<- as.data.frame(lstvarsselected1.3_fabric[["lstCoefAdoptmin"]])
#df3.3v<- as.data.frame(lstvarsselected1.3_verband[["lstCoefAdoptmin"]])
df1.4<- as.data.frame(lstvarsselected1.4_fabric[["lstCoefAdoptmin"]])
df1.5<- as.data.frame(lstvarsselected1.5_fabric[["lstCoefAdoptmin"]])
df1.6<- as.data.frame(lstvarsselected1.6_fabric[["lstCoefAdoptmin"]])
#df3.7<- as.data.frame(lstvarsselected1.7_fabric[["lstCoefAdoptmin"]])

library(qpcR)
VarsSelectedStep1 <-qpcR:::cbind.na (df1.0f, df1.0v,df1.1f, df1.2f, df1.3f, df1.4,df1.5,df1.6)

write_xlsx(VarsSelectedStep1,"VarsSelectedStep1_06.09.xlsx")

stargazer(VarsSelectedStep1,                 # Export txt
          summary = FALSE,
        type = "html",
          out = "VarsSelectedStep1Lasso.html")

#identify vars only chosen in step 2 (info)
#identify vars only chosen in step 1 (adoption)
df1.0f<- as.data.frame(lstvarsselected1.0_fabric[["lstCoefinfomin"]])
df1.0v<- as.data.frame(lstvarsselected1.0_verband[["lstCoefinfomin"]])
df1.1f<- as.data.frame(lstvarsselected1.1_fabric[["lstCoefinfomin"]])
#df1.1v<- as.data.frame(lstvarsselected1.1_verband[["lstCoefinfomin"]])
df1.2f<- as.data.frame(lstvarsselected1.2_fabric[["lstCoefinfomin"]])
#df1.2v<- as.data.frame(lstvarsselected1.2_verband[["lstCoefinfomin"]])
df1.3f<- as.data.frame(lstvarsselected1.3_fabric[["lstCoefinfomin"]])
#df1.3v<- as.data.frame(lstvarsselected1.3_verband[["lstCoefinfomin"]])
df1.4<- as.data.frame(lstvarsselected1.4_fabric[["lstCoefinfomin"]])
df1.5<- as.data.frame(lstvarsselected1.5_fabric[["lstCoefinfomin"]])
df1.6<- as.data.frame(lstvarsselected1.6_fabric[["lstCoefinfomin"]])
#df1.7<- as.data.frame(lstvarsselected1.7_fabric[["lstCoefinfomin"]])


VarsSelectedStep2 <-qpcR:::cbind.na (df1.0f, df1.0v,df1.1f, df1.2f, df1.3f, df1.4,df1.5,df1.6)

write_xlsx(VarsSelectedStep2,"VarsSelectedStep2_06.09.xlsx")

stargazer(VarsSelectedStep2,                 # Export txt
          summary = FALSE,
        type = "html",
          out = "VarsSelectedStep2Lasso.html")

```
create dataframe of estimates for info and field to average it then
```{r}
coefs_1.0_fabric_copy <- as.data.frame(coefs_1.0_fabric)
coefs_1.0_fabric_copy<-coefs_1.0_fabric_copy[-c(2:4)]
coefs_1.0_fabric_copy$names <- rownames(coefs_1.0_fabric_copy)

coefs_1.0_verband_copy <- as.data.frame(coefs_1.0_verband)
coefs_1.0_verband_copy<-coefs_1.0_verband_copy[-c(2:4)]
coefs_1.0_verband_copy$names <- rownames(coefs_1.0_verband_copy)

coefs_1.1_fabric_copy <- as.data.frame(coefs_1.1_fabric)
coefs_1.1_fabric_copy<-coefs_1.1_fabric_copy[-c(2:4)]
coefs_1.1_fabric_copy$names <- rownames(coefs_1.1_fabric_copy)

coefs_1.2_fabric_copy <- as.data.frame(coefs_1.2_fabric)
coefs_1.2_fabric_copy<-coefs_1.2_fabric_copy[-c(2:4)]
coefs_1.2_fabric_copy$names <- rownames(coefs_1.2_fabric_copy)

coefs_1.3_fabric_copy <- as.data.frame(coefs_1.3_fabric)
coefs_1.3_fabric_copy<-coefs_1.3_fabric_copy[-c(2:4)]
coefs_1.3_fabric_copy$names <- rownames(coefs_1.3_fabric_copy)

coefs_1.4_fabric_copy <- as.data.frame(coefs_1.4_fabric)
coefs_1.4_fabric_copy<-coefs_1.4_fabric_copy[-c(2:4)]
coefs_1.4_fabric_copy$names <- rownames(coefs_1.4_fabric_copy)

coefs_1.5_fabric_copy <- as.data.frame(coefs_1.5_fabric)
coefs_1.5_fabric_copy<-coefs_1.5_fabric_copy[-c(2:4)]
coefs_1.5_fabric_copy$names <- rownames(coefs_1.5_fabric_copy)

coefs_1.6_fabric_copy <- as.data.frame(coefs_1.6_fabric)
coefs_1.6_fabric_copy<-coefs_1.6_fabric_copy[-c(2:4)]
coefs_1.6_fabric_copy$names <- rownames(coefs_1.6_fabric_copy)


df.Coefficients_Lasso <- full_join(coefs_1.0_fabric_copy, coefs_1.0_verband_copy, by = "names")
df.Coefficients_Lasso <- full_join(df.Coefficients_Lasso, coefs_1.1_fabric_copy, by = "names")
df.Coefficients_Lasso <- full_join(df.Coefficients_Lasso, coefs_1.2_fabric_copy, by = "names")
df.Coefficients_Lasso <- full_join(df.Coefficients_Lasso, coefs_1.3_fabric_copy, by = "names")
df.Coefficients_Lasso <- full_join(df.Coefficients_Lasso, coefs_1.4_fabric_copy, by = "names")
df.Coefficients_Lasso <- full_join(df.Coefficients_Lasso, coefs_1.5_fabric_copy, by = "names")
df.Coefficients_Lasso <- full_join(df.Coefficients_Lasso, coefs_1.6_fabric_copy, by = "names")



#reorder
df.Coefficients_Lasso<-df.Coefficients_Lasso[,c(2,1,3:9)]
df.Coefficients_Lasso$mean_coef <- rowMeans(df.Coefficients_Lasso[,2:9], na.rm = TRUE)

#adjust col name sto models
df.Coefficients_Lasso <- dplyr::rename(df.Coefficients_Lasso, "Variable"= 1, "1.0_fabric"= 2, "1.0_verband"= 3,"1.1_fabric"= 4,"1.2_fabric" =5,"1.3_fabric" =6,"1.4_fabric" =7,"1.5_fabric" =8,"1.6_fabric" =9, "mean_coef"=10)

write_xlsx(df.Coefficients_Lasso,"Lasso_coefficients_06.09.xlsx")




```


